Best Practices in Latent Class Analysis using Free Open Source Software

### 2022-12-01 manuscript.Rmd
update 2022-12-01 15:26:44

### 
An extension of LCA is that containing covariates which can be used to
predict class membership. In this approach, we not only model the latent
class variable based on indicators, but we also relate the class
membership to other explanatory variables (@vermunt_latent_2017). An
example of using covariates comes from @nozadi_moderating_2016 who
applied LCA to identify the probability of children's membership to an
anxiety class. The authors tested several covariates including
children's age, sex, and accuracy scores. Age and sex were not found to
be related to the children's latent class membership, hence these
covariates were excluded from the analysis. Accuracy scores, however,
were related to probabilities of being in anxiety and attention-anxiety
classes. Therefore this covariate was kept as a valuable predictor.
Another example comes from @van_lissa_divergence_2015 who included sex 
as a predictor of the developmental trajectories and class membership in 
the previously discussed adolescent empathy development study. The rationale
was that adding sex as a covariate would account for known sex differences 
in empathy development, and lead to a model with lower bias.

@@

@@

>>>>

### Violations of normality

@@

### Controlling for covariates

An extension of LCA is that containing covariates which can be used to
predict class membership. In this approach, we not only model the latent
class variable based on indicators, but we also relate the class
membership to other explanatory variables (@vermunt_latent_2017). An
example of using covariates comes from @nozadi_moderating_2016 who
applied LCA to identify the probability of children's membership to an
anxiety class. The authors tested several covariates including
children's age, sex, and accuracy scores. Age and sex were not found to
be related to the children's latent class membership, hence these
covariates were excluded from the analysis. Accuracy scores, however,
were related to probabilities of being in anxiety and attention-anxiety
classes. Therefore this covariate was kept as a valuable predictor.
Another example comes from @van_lissa_divergence_2015 who included sex 
as a predictor of the developmental trajectories and class membership in 
the previously discussed adolescent empathy development study. The rationale
was that adding sex as a covariate would account for known sex differences 
in empathy development, and lead to a model with lower bias.

### Distal outcomes

@@

## Myths and misunderstandings

<!-- Treating ordinal data as continuous -->
<!-- People omitting the 1-class solution in class enumeration -->
